Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: Empirical Study of strategies in the Moran process for the Iterated Prisoner's

### 2018-01-11 second_response_to_reviewers.tex

- Suppose 10 people decide to play an IPD game. The authors only allowed pairs of
strategies in the population. If k individuals happen to pick the same strategy, what
is the likelihood the other 10 − k people will pick the same alternative strategy?
- The strategies evolved under a Moran process. Under a Moran process each round
one player must change his strategy 1 . Is there an example of a real-world social
dilemma or a human experiment where strategy changes resulted from a Moran pro-
cess or something similar? (This issue is particularly important because the authors
specifically trained some IPD strategies to excel at the Moran process.)
\end{verbatim}

This is the standard Moran process and the reviewer is asking about one of
the many extensions of the standard process, e.g. to multi-strategy populations
or other dynamics (such as a best-reply dynamic) which may allow players to
dynamically choose new strategies each round. The standard is an evolutionary
game where players have a fixed strategy throughout their lives with the
biological analogy of bacteria with different genetically coded traits and also
cancer, the latter of which is referenced in the introduction.

\begin{verbatim}
Suppose the population is using either strategy A or strategy B. Mutation was
not
allowed in the authors’ simulation so no other strategies can be used. How
useful then
is it to know some other strategy C can successfully invade strategy B if
strategy C
isn’t available?
\end{verbatim}

In biological situations it's often assumed that mutations are relatively rare
so it makes sense to run a process to fixation rather than look at many variants
at once in that context. In fact, the rate of mutation is typically set to 1 /
N, and the population runs for O(N) iterations before converging to one of the
absorbing states (and often far fewer), so there would typically be very few
simultaneous existing mutations. There are other contexts where there would be
more than two strategies at a time and they are interesting, but not the focus
of this work.

### 2018-01-11 main.tex
Add final edits from Marc.

This work uses pair-wise Moran processes in a similar way to matches in the many
IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
This work offers a population-based perspective which adds additional
evolutionary components to the IPD, namely the evolutionary dynamics of invasion
and resistance

>>>>

This work uses pair-wise Moran processes in a similar way to matches in the many
IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
A population-based perspective is given which adds additional
evolutionary components to the IPD, namely the evolutionary dynamics of invasion
and resistance.
